Beyond body length: Uncovering the drivers of vertebra number variation in Australian blindsnakes

### 2024-12-02 manuscript.Rmd
update

### Relationships between vertebra ratio, number of vertebrae, and aspect ratio
We found that vertebra ratio is positively correlated with mean aspect ratio (PGLS, slope = -0.0048, intercept = 0.73, R^2^ = 0.17, F = 7.09, Z = 2.20, P = 0.011), indicating that species that are more narrow-and-long usually have relatively more vertebrae for their length than species that are wide-and-robust (Fig. \@ref(fig:fig-vert-aspect-ratios) and Fig. S1). We also found that the mean number of vertebrae positively correlated with aspect ratio (PGLS, slope = -1.8, intercept = 120.95, R^2^ = 0.69, F = 79.39, Z = 5.30, P<0.001).

>>>>

### Relationships between vertebra ratio, number of vertebrae, and aspect ratio
We found that vertebra ratio is positively correlated with mean aspect ratio (PGLS, slope = 0.0048, intercept = 0.73, R^2^ = 0.17, F = 7.09, Z = 2.20, P = 0.011), indicating that species that are more narrow-and-long usually have relatively more vertebrae for their length than species that are wide-and-robust (Fig. \@ref(fig:fig-vert-aspect-ratios) and Fig. S1). We also found that the mean number of vertebrae positively correlated with aspect ratio (PGLS, slope = 1.8, intercept = 120.95, R^2^ = 0.69, F = 79.39, Z = 5.30, P<0.001).
